When does vapor pressure deficit drive or reduce evapotranspiration?

### 2017-12-18 doc/agu_2017/vpd.tex
found typo in agu presentation, fixed now
confirmed fig05 good and refactored, but ntoe that I broke the paper version a little for the agu talk so I need to fix this (conversion from Pa to kPa)

\section{Method}
\begin{frame}{Develop a theory to quantify VPD effects}
  \begin{itemize}
  \item The goal is to simply the problem (increase transparency) while still capturing the leading order behavior the system.
    \begin{itemize}
    \item Simplifying the system aids intrinsic understanding, but at a physical realism.
    \end{itemize}
  \item Because we run the risk of over-simplification, we will use FLUXNET2015 data to test how well our theory matches the data.
    \begin{itemize}
    \item We will test in the growing season of 5 plant types: Deciduous broadleaf forest, evergreen needleleaf forest, shrub, grass, and crops.
    \end{itemize}
  \end{itemize}
\end{frame}

@@

\section{Extra Slides}

\begin{frame}{Extra slide - statistics}
  \begin{table}
    \label{vpd_crit}
    \caption{More quantitative test of theory.}
    \centering
    \begin{tabular}{l c c c c c c}
      \hline
      PFT & \specialcell{Fraction of Obs.\\Theory is Correct} & Mean ($\frac{\partial \; ET}{\partial \; VPD} < 0$) & Mean ($\frac{\partial \; ET}{\partial \; VPD} > 0$)\\
      \hline
      CRO & 0.566517 & -0.209152 &  0.005856\\
      CSH & 0.931660 & -0.264746 &       NaN\\
      DBF & 0.633363 & -0.135679 &  0.042910\\
      ENF & 0.633138 & -0.150665 &  0.029281\\
      GRA & 0.442306 & -0.042158 & -0.042480\\
      \hline
    \end{tabular}
  \end{table}
\end{frame}

\begin{frame}{Quantitative $VPD_{crit}$}

  \scriptsize
  \begin{table}
    \label{vpd_crit}
    \caption{Values of $VPD_{crit}$, where $\frac{\partial \; ET}{\partial \; VPD} = 0$, evaluated at PFT average values for $R_{air}$, $\sigma$, $\gamma$, and $c_s$. For reference, these values are also provided. For values of $VPD$ less than $VPD_{crit}$, $\frac{\partial \; ET}{\partial \; VPD}$ will be negative, and for values of $VPD$ greater than $VPD_{crit}$, $\frac{\partial \; ET}{\partial \; VPD}$ will be positive.}
    \centering
    \begin{tabular}{l c c c c c}
      \hline
      PFT & $R_{air}$ & $c_s$ (ppm) & $\gamma$ &  uWUE & \textbf{$VPD_{crit}$ (Pa)} \\
      \hline
      CRO &  288.680920 & 372.567691& 65.351523& 2.602873&  \textbf{133.165438} \\
      CSH &   289.067152& 381.593622& 67.613172& 2.175278& \textbf{4439.564212} \\
      DBF &   288.624437& 377.449849& 63.421812& 2.746393&  \textbf{888.773243} \\
      ENF &  288.183849& 377.676463& 61.559242& 4.015362&  \textbf{978.084845} \\
      GRA &  288.425651& 377.264645& 61.598768& 2.281074& \textbf{1141.630778} \\
      \hline
      \multicolumn{2}{l}{}
    \end{tabular}
  \end{table}
\end{frame}

\begin{frame}{Statistics with uncertainty}
  \scriptsize
  \begin{table}
    \caption{Statistics of $\frac{\partial \; ET}{\partial \; VPD}$ as a function of PFT.}
    \centering
    \begin{tabular}{l c c c c c}
      \hline
      PFT & $\overline{\frac{\partial \; ET}{\partial \; VPD}}$ & $\frac{\partial \; ET}{\partial \; VPD}\left(\overline{env}\right)$ & $\frac{\partial \; ET}{\partial \; VPD}\left(\overline{env}\right)*\text{std}(VPD)$ & $\frac{\frac{\partial \; ET}{\partial \; VPD}\left(\overline{env}\right)*\text{std}(VPD)}{ \frac{\partial \; ET}{\partial \; R}\left(\overline{env}\right)*\text{std}(R)}$ & fraction $\frac{\partial \; ET}{\partial \; VPD} < 0.$ \\
      \hline
      CRO & 0.000853 & 0.026241 & 37.05 & 0.41 & 0.473311\\
      CSH & -0.108234 & -0.091526 & 101.72 & 0.88 & 0.931660\\
      DBF & -0.012727 & 0.013794 & 39.47 & 0.33 & 0.461674\\
      ENF & -0.034087 & 0.000706 & 33.22 & 0.30 & 0.534425\\
      GRA & -0.019637 & -0.000921 & 33.60 & 0.35 & 0.631735\\
      \hline
      \multicolumn{2}{l}{}

    \end{tabular}
  \end{table}
\end{frame}

\begin{frame}{Scaling Term}
  \[\frac{\partial \;  ET}{\partial \; D} = \mathbf{ \frac{g_a \; P}{T(\Delta + \gamma)} }   \left(\frac{ c_p}{R_{air}} - \frac{\text{LAI$_{ref}$}}{\text{LAI}} \frac{\gamma c_s }{1.6 \; R*\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D}}{2 (g_1 + \sqrt{D})^2}\right) \right)\]
  \begin{figure}
    \includegraphics[width=3.0in]{scaling.png}
    % \caption{}
  \end{figure}
\end{frame}

\begin{frame}{Extra slide - is theory VPD$_{crit}$ optimum?}
  \includegraphics[width=0.7\textwidth]{for_agu.pdf}
\end{frame}

\begin{frame}{Test theory with FLUXNET data - CSH}
  \includegraphics[width=3.5in]{csh_eee.png}
\end{frame}

\begin{frame}{Test theory with FLUXNET data - ENF}
  \includegraphics[width=3.5in]{enf_eee.png}
\end{frame}

\begin{frame}{Test theory with FLUXNET data - DBF}
  \includegraphics[width=3.5in]{dbf_eee.png}
\end{frame}

\begin{frame}{Test theory with FLUXNET data - CRO}
  \includegraphics[width=3.5in]{cro_eee.png}
\end{frame}

\begin{frame}{Test theory with FLUXNET data - GRA}
  \includegraphics[width=3.5in]{gra_eee.png}
\end{frame}

\begin{frame}{Is uncertainty a function of VPD?}
  \includegraphics[width=3.0in]{vpd_sigma.png}
\end{frame}

\begin{frame}{How to take VPD derivative?}
  % below gnereated in fig03.py
  \includegraphics[width=3.0in]{e_s_rh.png}
\end{frame}

% \begin{frame}{Summary statistics - extra sl}
%   \begin{table}
%     \caption{Statistics of $\frac{\partial \; ET}{\partial \, VPD}$ as a function of PFT.}
%     \centering
%     \begin{tabular}{l c c}
%       \hline
%       PFT & $\overline{\frac{\partial \; ET}{\partial \; VPD}}$ & fraction $\frac{\partial \; ET}{\partial \; VPD} < 0.$ \\
%       \hline
%       CRO & 0.000853  & 0.473311\\
%       CSH & -0.108234 & 0.931660\\
%       DBF & -0.012727 & 0.461674\\
%       ENF & -0.034087 & 0.534425\\
%       GRA & -0.019637 & 0.631735\\
%       \hline
%       \multicolumn{2}{l}{}  
%     \end{tabular}
%   \end{table}
% \end{frame}

% \begin{table}
%   \centering
%   \begin{tabular}{l|r}
%     Item & Quantity \\\hline
%     Widgets & 42 \\
%     Gadgets & 13
%   \end{tabular}
%   \caption{\label{tab:widgets}An example table.}
% \end{table}

>>>>

\section{Method}
\begin{frame}{Develop a theory to quantify ET response to VPD}
  \begin{itemize}
  \item The goal is to simply the problem (increase transparency) while still capturing the leading order behavior the system.
    \begin{itemize}
    \item Simplifying the system aids intrinsic understanding, but at a physical realism cost.
    \end{itemize}
  \item Because we run the risk of over-simplification, we will use FLUXNET2015 data to test how well our theory matches the data.
    \begin{itemize}
    \item We will test in the growing season of 5 plant types: deciduous broadleaf forest, evergreen needleleaf forest, shrub, grass, and crops.
    \end{itemize}
  \end{itemize}
\end{frame}

@@

\begin{frame}{Summary - When does VPD drive or reduce ET?}
  \begin{itemize}
  \item Theory predicts that each plant type has a \textbf{critical VPD} \textbf{below which ET will decrease} (plant response dominates), and \textbf{above which ET will increase} (atmospheric demand dominates).
  \item For forest sites, environmental VPD approximately straddles the critical VPD.
  \item For shrubs environmental VPD never exceeds the critical VPD.
  \item Theory tested poorly with FLUXNET data for for crops and grass. 
  \item All plant types exhibited a response far below that of PET.
  \item The new uWUE-version of Penman-Monteith we derived could be used as a complement for PET in drought indices over vegetated surfaces.
  \end{itemize}
  \bigskip
  \medskip
  Adam Massmann:\textbf{ akm2203@columbia.edu }
\end{frame}

% \section{Extra Slides}

% \begin{frame}{Extra slide - statistics}
%   \begin{table}
%     \label{vpd_crit}
%     \caption{More quantitative test of theory.}
%     \centering
%     \begin{tabular}{l c c c c c c}
%       \hline
%       PFT & \specialcell{Fraction of Obs.\\Theory is Correct} & Mean ($\frac{\partial \; ET}{\partial \; VPD} < 0$) & Mean ($\frac{\partial \; ET}{\partial \; VPD} > 0$)\\
%       \hline
%       CRO & 0.566517 & -0.209152 &  0.005856\\
%       CSH & 0.931660 & -0.264746 &       NaN\\
%       DBF & 0.633363 & -0.135679 &  0.042910\\
%       ENF & 0.633138 & -0.150665 &  0.029281\\
%       GRA & 0.442306 & -0.042158 & -0.042480\\
%       \hline
%     \end{tabular}
%   \end{table}
% \end{frame}

% \begin{frame}{Quantitative $VPD_{crit}$}

%   \scriptsize
%   \begin{table}
%     \label{vpd_crit}
%     \caption{Values of $VPD_{crit}$, where $\frac{\partial \; ET}{\partial \; VPD} = 0$, evaluated at PFT average values for $R_{air}$, $\sigma$, $\gamma$, and $c_s$. For reference, these values are also provided. For values of $VPD$ less than $VPD_{crit}$, $\frac{\partial \; ET}{\partial \; VPD}$ will be negative, and for values of $VPD$ greater than $VPD_{crit}$, $\frac{\partial \; ET}{\partial \; VPD}$ will be positive.}
%     \centering
%     \begin{tabular}{l c c c c c}
%       \hline
%       PFT & $R_{air}$ & $c_s$ (ppm) & $\gamma$ &  uWUE & \textbf{$VPD_{crit}$ (Pa)} \\
%       \hline
%       CRO &  288.680920 & 372.567691& 65.351523& 2.602873&  \textbf{133.165438} \\
%       CSH &   289.067152& 381.593622& 67.613172& 2.175278& \textbf{4439.564212} \\
%       DBF &   288.624437& 377.449849& 63.421812& 2.746393&  \textbf{888.773243} \\
%       ENF &  288.183849& 377.676463& 61.559242& 4.015362&  \textbf{978.084845} \\
%       GRA &  288.425651& 377.264645& 61.598768& 2.281074& \textbf{1141.630778} \\
%       \hline
%       \multicolumn{2}{l}{}
%     \end{tabular}
%   \end{table}
% \end{frame}

% \begin{frame}{Statistics with uncertainty}
%   \scriptsize
%   \begin{table}
%     \caption{Statistics of $\frac{\partial \; ET}{\partial \; VPD}$ as a function of PFT.}
%     \centering
%     \begin{tabular}{l c c c c c}
%       \hline
%       PFT & $\overline{\frac{\partial \; ET}{\partial \; VPD}}$ & $\frac{\partial \; ET}{\partial \; VPD}\left(\overline{env}\right)$ & $\frac{\partial \; ET}{\partial \; VPD}\left(\overline{env}\right)*\text{std}(VPD)$ & $\frac{\frac{\partial \; ET}{\partial \; VPD}\left(\overline{env}\right)*\text{std}(VPD)}{ \frac{\partial \; ET}{\partial \; R}\left(\overline{env}\right)*\text{std}(R)}$ & fraction $\frac{\partial \; ET}{\partial \; VPD} < 0.$ \\
%       \hline
%       CRO & 0.000853 & 0.026241 & 37.05 & 0.41 & 0.473311\\
%       CSH & -0.108234 & -0.091526 & 101.72 & 0.88 & 0.931660\\
%       DBF & -0.012727 & 0.013794 & 39.47 & 0.33 & 0.461674\\
%       ENF & -0.034087 & 0.000706 & 33.22 & 0.30 & 0.534425\\
%       GRA & -0.019637 & -0.000921 & 33.60 & 0.35 & 0.631735\\
%       \hline
%       \multicolumn{2}{l}{}

%     \end{tabular}
%   \end{table}
% \end{frame}

% \begin{frame}{Scaling Term}
%   \[\frac{\partial \;  ET}{\partial \; D} = \mathbf{ \frac{g_a \; P}{T(\Delta + \gamma)} }   \left(\frac{ c_p}{R_{air}} - \frac{\text{LAI$_{ref}$}}{\text{LAI}} \frac{\gamma c_s }{1.6 \; R*\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D}}{2 (g_1 + \sqrt{D})^2}\right) \right)\]
%   \begin{figure}
%     \includegraphics[width=3.0in]{scaling.png}
%     % \caption{}
%   \end{figure}
% \end{frame}

% \begin{frame}{Extra slide - is theory VPD$_{crit}$ optimum?}
%   \includegraphics[width=0.7\textwidth]{for_agu.pdf}
% \end{frame}

% \begin{frame}{Test theory with FLUXNET data - CSH}
%   \includegraphics[width=3.5in]{csh_eee.png}
% \end{frame}

% \begin{frame}{Test theory with FLUXNET data - ENF}
%   \includegraphics[width=3.5in]{enf_eee.png}
% \end{frame}

% \begin{frame}{Test theory with FLUXNET data - DBF}
%   \includegraphics[width=3.5in]{dbf_eee.png}
% \end{frame}

% \begin{frame}{Test theory with FLUXNET data - CRO}
%   \includegraphics[width=3.5in]{cro_eee.png}
% \end{frame}

% \begin{frame}{Test theory with FLUXNET data - GRA}
%   \includegraphics[width=3.5in]{gra_eee.png}
% \end{frame}

% \begin{frame}{Consequences of theory - ``sign'' term}
% Below is a little opaque (at least to me):
% \[\frac{\partial \, ET}{\partial \, VPD} = \text{scaling} \cdot  \left(\frac{ c_p}{R_{air}} - \frac{\gamma c_s }{1.6 \; R*\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{VPD}}{2 (g_1 + \sqrt{VPD})^2}\right) \right)\]
% so do expansion about $g_1 >> \sqrt{VPD}$:
% \footnotesize
% \[ \frac{\partial \, ET}{\partial \, VPD} \approx \text{scaling} \cdot  \left(\frac{ c_p}{R_{air}} - \frac{\gamma c_s }{1.6 \; R*\; \text{ uWUE }} \left( \frac{1}{g_1} - \frac{3\sqrt{VPD}}{2 g_1^2} +  \mathcal{O}\left(\frac{\sqrt{VPD}}{g_1}\right)^{2} \right) \right)\]
% % \large
% % and:
% %   \[ \sqrt{VPD} \Big|_{\frac{\partial ET}{\partial VPD} = 0} \approx  \frac{2 g_1}{3}  \left( -\frac{ c_p \, g_1\,  1.6  \; R*\; \text{ uWUE }}{R_{air} \gamma c_s } + 1  \right) \]

% %   \[ VPD \Big|_{\frac{\partial ET}{\partial VPD} = 0} = \frac{R_{air}}{4 \, c_p} \left[ \frac{\gamma  c_s}{R* \, 1.6\, \text{uWUE}} + \sqrt{\left(g_1 + 8\, \frac{c_p}{R_{air}}\right) \frac{\gamma c_s}{R* \, 1.6\, \text{uWUE}}} - 4 \, g_1 \frac{ c_p}{R_{air}}\right] \]
% \end{frame}

% \begin{frame}{Is uncertainty a function of VPD?}
%   \includegraphics[width=3.0in]{vpd_sigma.png}
% \end{frame}

% \begin{frame}{How to take VPD derivative?}
%   % below gnereated in fig03.py
%   \includegraphics[width=3.0in]{e_s_rh.png}
% \end{frame}

% % \begin{frame}{Summary statistics - extra sl}
% %   \begin{table}
% %     \caption{Statistics of $\frac{\partial \; ET}{\partial \, VPD}$ as a function of PFT.}
% %     \centering
% %     \begin{tabular}{l c c}
% %       \hline
% %       PFT & $\overline{\frac{\partial \; ET}{\partial \; VPD}}$ & fraction $\frac{\partial \; ET}{\partial \; VPD} < 0.$ \\
% %       \hline
% %       CRO & 0.000853  & 0.473311\\
% %       CSH & -0.108234 & 0.931660\\
% %       DBF & -0.012727 & 0.461674\\
% %       ENF & -0.034087 & 0.534425\\
% %       GRA & -0.019637 & 0.631735\\
% %       \hline
% %       \multicolumn{2}{l}{}  
% %     \end{tabular}
% %   \end{table}
% % \end{frame}

% % \begin{table}
% %   \centering
% %   \begin{tabular}{l|r}
% %     Item & Quantity \\\hline
% %     Widgets & 42 \\
% %     Gadgets & 13
% %   \end{tabular}
% %   \caption{\label{tab:widgets}An example table.}
% % \end{table}

### 2017-12-18 doc/paper/vpd_et_paper.tex
think done with rough draft
confirmed fig05 good and refactored, but ntoe that I broke the paper version a little for the agu talk so I need to fix this (conversion from Pa to kPa)

\begin{linenomath*}
  \begin{equation}
    \label{uwue}
uWUE = \frac{GPP \cdot \sqrt{VPD}{ET}
  \end{equation}
\end{linenomath*}
is relatively constant across time and space (within plant functional type). If, following \citet{Lin_2015}, we approximate $g_0$ as $0$, we can use uWUE to remove $A$ from $g_s$ in a way that makes PM analytically tractable:

@@

\begin{table}
\caption{Statistics of $\frac{\partial \; ET}{\partial \; VPD}$ as a function of PFT.}
\centering
\begin{tabular}{l c c c c c}
  \hline
PFT & $\overline{\frac{\partial \; ET}{\partial \; VPD}}$ & $\frac{\partial \; ET}{\partial \; VPD}\left(\overline{T, \ldots , VPD}\right)$ & $\frac{\partial \; ET}{\partial \; VPD}\left(\overline{T, \ldots , VPD}\right)*\text{std}(VPD)$ & $\frac{\frac{\partial \; ET}{\partial \; VPD}\left(\overline{T, \ldots , VPD}\right)*\text{std}(VPD)}{ \frac{\partial \; ET}{\partial \; R}\left(\overline{T, \ldots , VPD}\right)*\text{std}(R)}$ & fraction $\frac{\partial \; ET}{\partial \; VPD} < 0.$ \\
  \hline
CRO & 0.000853 & 0.026241 & 18.523659 & 0.203022 & 0.473311\\
CSH & -0.108234 & -0.091526 & 50.861613 & 0.439379 & 0.931660\\
DBF & -0.012727 & 0.013794 & 19.734435 & 0.164241 & 0.461674\\
ENF & -0.034087 & 0.000706 & 16.611852 & 0.148548 & 0.534425\\
GRA & -0.019637 & -0.000921 & 16.798083 & 0.173552 & 0.631735\\
\hline
\multicolumn{2}{l}{$^{a}$Footnote text here.}

@@

In general the full complexity plots of $\frac{\partial \; ET}{\partial \; VPD}$ match our expectations, even with the large sensitivity to $\sigma$ measures of uncertainty observed in Figure \ref{term3}. Our $\sigma$-based method of uncertainty propagation blurs the idealized expectations the most for GRA, and also has a considerable effect for CRO. We therefor have the most confidence in our conclusion based on Equation \ref{d_et} for PFTS CSH, DBF, and ENF, as the full complexity plots with uncertainty included closely match the story when $\sigma$ is held fixed. **see somewhat preferred alternate figure \ref{real2} \explain{I think I like the alternate plot much  more as thinking in terms of T and RH is easier, and it makes the story easier to see at relatively low temperatures. However, I used the other plot because Fig 5 does not discuss things in terms of temperature, as this would make things more complicated (adding another dimension). I could just include both versions of figure 6 though (using figure 6a as a bridge to figure 6b)}.
\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{./fig06.png}
\caption{Scatter plots of $\frac{\partial \; ET}{\partial \; VPD}$. Each row is a different PFT, and each column is a different quantity related to $\frac{\partial \; ET}{\partial \; VPD}$, as labeled: Column 1 - $\frac{\partial \; ET}{\partial \; VPD}$; Column 2 - $\frac{\partial \; ET}{\partial \; VPD}$ normalized by $g_a$; Column 3 - $\frac{\partial \; ET}{\partial \; VPD}$ with $\sigma$ held fixed at PFT average; and Column 4 - $\frac{\partial \; ET}{\partial \; VPD}$ normalized by $g_a$ and with $\sigma$ held fixed. For reference, lines corresponding to RH = 20\% and RH = 90 \% are drawn. Please note differences in the colorbar scale. ***see alternate (or additional) plot below.***}
\label{real}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{./fig06b.png}
\caption{****alternate Fig 06****  Scatter plots of $\frac{\partial \; ET}{\partial \; VPD}$. Each row is a different PFT, and each column is a different quantity related to $\frac{\partial \; ET}{\partial \; VPD}$, as labeled. If I end up using this, I could also draw on the curve of $VPD_{crit}$ with $\overline{\frac{\text{LAI}}{\text{LAI$_{ref}$}}}$. }
\label{real2}
\end{figure}

>>>>

\begin{linenomath*}
  \begin{equation}
    \label{uwue}
uWUE = \frac{GPP \cdot \sqrt{VPD}}{ET}
  \end{equation}
\end{linenomath*}
is relatively constant across time and space (within plant functional type). If, following \citet{Lin_2015}, we approximate $g_0$ as $0$, we can use uWUE to remove $A$ from $g_s$ in a way that makes PM analytically tractable:

@@

\begin{table}
\caption{Statistics of $\frac{\partial \; ET}{\partial \; VPD}$ as a function of PFT.}
\centering
\begin{tabular}{l c c c c c}
  \hline
PFT & $\overline{\frac{\partial \; ET}{\partial \; VPD}}$ & $\frac{\partial \; ET}{\partial \; VPD}\left(\overline{env}\right)$ & $\frac{\partial \; ET}{\partial \; VPD}\left(\overline{env}\right)*\text{std}(VPD)$ & $\frac{\frac{\partial \; ET}{\partial \; VPD}\left(\overline{env}\right)*\text{std}(VPD)}{ \frac{\partial \; ET}{\partial \; R}\left(\overline{env}\right)*\text{std}(R)}$ & fraction $\frac{\partial \; ET}{\partial \; VPD} < 0.$ \\
  \hline
CRO & 0.000853 & 0.026241 & 37.05 & 0.41 & 0.473311\\
CSH & -0.108234 & -0.091526 & 101.72 & 0.88 & 0.931660\\
DBF & -0.012727 & 0.013794 & 39.47 & 0.33 & 0.461674\\
ENF & -0.034087 & 0.000706 & 33.22 & 0.30 & 0.534425\\
GRA & -0.019637 & -0.000921 & 33.60 & 0.35 & 0.631735\\
\hline
\multicolumn{2}{l}{$^{a}$Footnote text here.}

@@

In general the full complexity plots of $\frac{\partial \; ET}{\partial \; VPD}$ match our expectations, even with the large sensitivity to $\sigma$ measures of uncertainty observed in Figure \ref{term3}. Our $\sigma$-based method of uncertainty propagation blurs the idealized expectations the most for GRA, and also has a considerable effect for CRO. We therefor have the most confidence in our conclusion based on Equation \ref{d_et} for PFTS CSH, DBF, and ENF, as the full complexity plots with uncertainty included closely match the story when $\sigma$ is held fixed. % **see somewhat preferred alterate figure \ref{real2} \explain{I think I like the alternate plot much  more as thinking in terms of T and RH is easier, and it makes the story easier to see at relatively low temperatures. However, I used the other plot because Fig 5 does not discuss things in terms of temperature, as this would make things more complicated (adding another dimension). I could just include both versions of figure 6 though (using figure 6a as a bridge to figure 6b)}.
\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{./fig06.png}
\caption{Scatter plots of $\frac{\partial \; ET}{\partial \; VPD}$. Each row is a different PFT, and each column is a different quantity related to $\frac{\partial \; ET}{\partial \; VPD}$, as labeled: Column 1 - $\frac{\partial \; ET}{\partial \; VPD}$; Column 2 - $\frac{\partial \; ET}{\partial \; VPD}$ normalized by $g_a$; Column 3 - $\frac{\partial \; ET}{\partial \; VPD}$ with $\sigma$ held fixed at PFT average; and Column 4 - $\frac{\partial \; ET}{\partial \; VPD}$ normalized by $g_a$ and with $\sigma$ held fixed. For reference, lines corresponding to RH = 20\% and RH = 90 \% are drawn. Please note differences in the colorbar scale. ***see alternate (or additional) plot below.***}
\label{real}
\end{figure}

% \begin{figure}[h]
% \centering
% \includegraphics[width=\textwidth]{./fig06b.png}
% \caption{****alternate Fig 06****  Scatter plots of $\frac{\partial \; ET}{\partial \; VPD}$. Each row is a different PFT, and each column is a different quantity related to $\frac{\partial \; ET}{\partial \; VPD}$, as labeled. If I end up using this, I could also draw on the curve of $VPD_{crit}$ with $\overline{\frac{\text{LAI}}{\text{LAI$_{ref}$}}}$. }
% \label{real2}
% \end{figure}
